Discrete Quantum Theories and Computing

### 2019-02-01 dissertation.tex
dissertation.lyx Review until "5.1.3 Classical Choquet integrals and Expectation Values of Observables", but I suddenly afraid the definition of expectation value of classical IVPM might be wrong... Need to check...

The part of the conventional quantum theory (CQT) used by quantum
circuit model is described by the following:
\begin{enumerate}[label=(\roman{enumi})]
\item \label{enu:-orthonormal-basis}$D$ orthonormal basis vectors for
a Hilbert space of dimension~$D$,
\item \label{enu:probability-amplitude}$D$ complex probability amplitude
coefficients describing the contribution of each basis vector,
\item \label{enu:unitary-matrix}a set of probability-conserving unitary
matrix operators that suffice to describe all required state transformations
of a quantum circuit,
\item \label{enu:measurement-framework}and a measurement framework.
\end{enumerate}
In Sec.~\ref{CQC1qubitBloch.sec}, we focus on the geometric issues
raised by the properties~\ref{enu:-orthonormal-basis} and~\ref{enu:probability-amplitude}
given above for CQT\@. In Sec.~\ref{sec:fuzzy}, we introduce the
important issues of~\ref{enu:measurement-framework} and the foundations
of quantum probability space. The expectation values defined in Sec.~\ref{sec:fuzzy}
will be used to understand the geometry of entangled states in Sec.~\ref{sec:The-geometry-of}.
The property~\ref{enu:unitary-matrix} directly related to quantum
circuits will be introduced later in Chapter~\ref{chap:DQT=000026DQC}
when we dive into quantum algorithms.

@@

For a two-dimensional system, we could easily solve the problem of
reducing the full unit-norm space to its irreducible components $\Hat{a}=\left(X,Y,Z\right)$
characterizing the Bloch sphere. We have just argued that essentially
the same process is possible for $D$-dimensional system: in the abstract
argument, we simply identify the family of coefficients $\left\{ \alpha_{i}\right\} $
as being the same if they differ only by an overall phase $\rme^{\rmi\theta}$.
However, in practice, this is not a construction that is easy to realize
in a practical computation. We now outline an explicit algorithm for
accomplishing the reduction to the irreducible $D$-dimensional state
space $\CP{D-1}$; this construction will turn out to be useful for
the validation of our discrete results to follow below.

Given a normalized pure state $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}$,
a natural quantity characterizing a $D$-dimensional system is its
\textit{density matrix}, $\rho=\op{\Psi}{\Psi}$, or 
\begin{equation}
\rho=\begin{pmatrix}|\alpha_{0}|^{2} & \alpha_{0}\alpha_{1}^{*} & \cdots & \alpha_{0}\alpha_{D-1}^{*}\\
\alpha_{1}\alpha_{0}^{*} & |\alpha_{1}|^{2} & \cdots & \alpha_{1}\alpha_{D-1}^{*}\\
\vdots & \vdots & \ddots & \vdots\\
\alpha_{D-1}\alpha_{0}^{*} & \cdots & \alpha_{D-1}\alpha_{D-2}^{*} & |\alpha_{D-1}|^{2}
\end{pmatrix}\,.\label{nqDensity.eq}
\end{equation}
We can now use the complex generalization of the classical Veronese
coordinate system for projective geometry to remove the overall phase
ambiguity $\rme^{\rmi\theta}$ from the $D$-dimensional states. If
we take a particular weighting of the elements of the density matrix~$\rho$,
we can construct a \textit{unit vector} of real dimension $D^{2}$
with the form: 
\begin{equation}
\Hat{a}=\left(|\alpha_{i}|^{2},\ldots,\sqrt{2}\,\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\,\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots\right)\,,\label{nqCoords.eq}
\end{equation}
where 
\[
\Hat{a}\cdot\Hat{a}=\sum_{i=0}^{D-1}\left(\left|\alpha_{i}\right|^{2}\right)^{2}+\sum_{i=0}^{D-1}\sum_{\substack{j=0\\
j\ne i
}
}^{D-1}\left(\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*}\right)^{2}+\left(\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*}\right)^{2}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)\left(\sum_{j=0}^{D-1}\left|\alpha_{j}\right|^{2}\right)=1\,.
\]
This construction gives an explicit embedding of the $\left(D-1\right)$-dimensional
complex, or $\left(2D-2\right)$-dimensional real, object in a real
space of dimension $D^{2}$. However, this is somewhat subtle because
the vector is of unit length, so technically the embedding space is
a sphere of dimension $D^{2}-1$ embedded in $\R^{D^{2}}$. For example,
the two-dimensional irreducible states could be represented in a four-dimensional
embedding, but the magnitude of every coordinate would be one; furthermore,
the object embedded in the resulting $\Sphere{3}$ is indeed $\Sphere{2}$
because we can fix one complex coordinate to be unity, and let one
vary, giving a total of two irreducible dimensions. In fact, one must
choose \textit{two} coordinate patches, one covering one pole of $\Sphere{2}$
with coordinates $\alpha_{0}=1+\rmi0$ and $\alpha_{1}=x_{1}+\rmi y_{1}$,
and the other patch covering the other pole of $\Sphere{2}$ with
coordinates $\alpha_{0}=x_{0}+\rmi y_{0}$ and $\alpha_{1}=1+\rmi0$.
\begin{comment}
\todo{Explain the last part clearer or add a picture.}
\end{comment}

@@

One special feature of quantum experiments is that the probabilities
in different experiments are correlated. Consider another experiment
sending exactly the same particle as the previous one but using a
different beam splitter corresponding to the observable $\mathbf{O}_{1}$
with spectral decomposition $\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$,
where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$.
Although the sample space $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $
and the probability measure $\mu_{1}\colon2^{\Omega_{1}}\rightarrow\left[0,1\right]$
defined by this experiment is different from the previous one, these
two experiments may produce the same post-experimental state~$\ket{2}$,
and the probability of the common event $\left\{ \ket{2}\right\} $
is believed to be the same, i.e., $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$.
In general, as long as sending the same particle, the probability
of the same event in different experiments should always be the same.
This fact is equivalent to the fact that commuting observables could
be measured simultaneously which is essential to define contextuality
and will be explained in Sec.~\ref{sec:Kochen-Specker}.

Since the probability induced by the different beam splitters are
correlated, it is more natural to define one quantum event space~$\events$
containing all possible classical event spaces using different beam
splitters. However, simply taking the union of all event spaces is
a bad idea because two events might appear different but representing
the same situation. For example, if we take the complement on both
sides of $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$,
we will have
\begin{equation}
\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
\end{equation}
that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same, and
these events should be identified as the same quantum event to simplify
our discussion. This identification can be achieved by mapping a classical
event~$E$ to the projector generated by $E$,
\begin{equation}
\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\label{eq:pullback-function}
\end{equation}
with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$, because
$\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)$ is equal to
$\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)$ as operators,
\begin{equation}
\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)=\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}=\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,.
\end{equation}
In general, if two classical events~$E$ and $E'$ are mapped to
the same projector, i.e., $\varphi\left(E\right)=\varphi\left(E'\right)$,
then the probability of $E$ is the same as the probability of $E'$.
Therefore, for any classical event~$E$, its corresponding quantum
event is defined to be the projector $\varphi\left(E\right)$, and
the set of all projectors on a given Hilbert space is called a quantum
event space~$\events$. %
\begin{comment}
\todo{Check the citation of this part. Did von Neumann really think
about this when he uses projectors to formulate the quantum theory?}
\end{comment}

@@

\begin{proof}By Eq.~(\ref{eq:quantum-expectation}), we have
\[
\expval{\mathbf{O}}_{\mu}=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(\proj{i}\right)=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(\varphi\left(\left\{ \ket{i}\right\} \right)\right)=\sum_{i=0}^{D-1}\lambda_{i}\left(\varphi^{*}\mu\right)\left(\left\{ \ket{i}\right\} \right)=\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\mu\right)\,.
\]
\end{proof}

@@

After introducing quantum probability measures, we might follow the
convention to introduce the Born rule which is the only way corresponding
a state to a quantum probability measure in CQT\@. However, since
the variants of quantum probability measures in Sec.~\ref{sec:Toward-IVPM}
and Chapter~\ref{chap:QIVPM} could not be constructed by the Born
rule easily, searching for a Born rule step-by-step here might provide
a better idea of what we should do in Sec.~\ref{sec:Toward-IVPM}
and Chapter~\ref{chap:QIVPM}. While the situations will become more
delicate in the later sections, we will, fortunately, find the unique
Born rule for CQT here.

@@

Let a pure unnormalized state $\ket{\Phi}\in\mathcal{H}$ characterize
the particle sending to a Stern-Gerlach type experiment, and $\muB_{\Phi}$
be the quantum probability measure of the resulting events sensibly
corresponding to $\ket{\Phi}$. For a correspondence $\ket{\Phi}\mapsto\muB_{\Phi}$
to be sensible, we hope that if the state~$\ket{\Phi}$ is one of
the outcomes of a quantum event~$P$, $P\ket{\Phi}=\ket{\Phi}$,
then the event~$P$ always happens, $\muB_{\Phi}\left(P\right)=1$,
and vice versa. Moreover, since the physical phenomena exist and should
be the same no matter how we describe them, the probability of an
event should be invariant despite how we choose the basis. Because
changing to another basis is the same as applying a unitary map~$U$,
we should have $\muB_{U\ket{\Phi}}\left(UPU^{\dagger}\right)=\muB_{\Phi}\left(P\right)$.
It is easy to check that the correspondence satisfying these conditions
is unique, 
\begin{equation}
\muB_{\Phi}(P)=\frac{\melem{\Phi}{P}{\Phi}}{\ip{\Phi}{\Phi}}\label{eq:Born}
\end{equation}
and called the Born rule \cite{Born1983,Mermin2007,Jaeger2007}. If
$\ket{\Phi}$ is normalized, Eq.~(\ref{eq:Born}) could be simplified
as $\muB_{\Phi}(P)=\melem{\Phi}{P}{\Phi}$. Since a mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$
is a weighted average of projectors $\proj{\Phi_{j}}$ with weights
$q_{j}>0$ and $\sum_{j=1}^{N}q_{j}=1$, the generalized Born rule
of $\rho$, $\muB_{\rho}\left(P\right)$, is also a weighted average
of $\muB_{\Phi_{j}}\left(P\right)$, 
\begin{equation}
\muB_{\rho}\left(P\right)=\sum_{j=1}^{N}q_{j}\muB_{\Phi_{j}}\left(P\right)=\Tr\left(\rho P\right)\,,\label{eq:mixed-Born}
\end{equation}
which is also a quantum probability measure and consistent with Gleason's
theorem.

As an example, consider a three-dimensional Hilbert space with orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $ and the observable
$\mathbf{O}_{0}$ defined in Eq.~(\ref{eq:observable}). Two fragments
of valid probability measures~$\mu_{1}$ and $\mu_{2}$ that can
be associated with this space are defined in Table~\ref{tab:quantum-probability-measure}.
By the Born rule, the first probability measure corresponds to the
quantum system being in the pure state $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$
and the second corresponds to the quantum system being in the state
$\frac{\proj{0}+\proj{2}}{2}$. The expectation values of the observable
$\mathbf{O}$, $\expval{\mathbf{O}}_{\mu_{1,2}}$, are $1.5$ in the
first case and $2$ in the second. The quantum expectation value can
also use to decide whether a state is entangled or not for multipartite
systems as we describe in the following section.
\begin{table}
\noindent \begin{centering}
\caption{\label{tab:quantum-probability-measure}Two fragments of valid probability
measures~$\mu_{1}$ and $\mu_{2}$.}
\par\end{centering}
\noindent \centering{}%
\begin{tabular}{ccccccccccc}
\toprule 
\addlinespace
$\ket{\Psi}$ & $\ket{0}$ & $\ket{1}$ & $\ket{2}$ & $\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ & $\frac{\ket{0}+\rmi\ket{1}}{\sqrt{2}}$ & $\frac{\ket{0}+\ket{2}}{\sqrt{2}}$ & $\frac{\ket{0}+\rmi\ket{2}}{\sqrt{2}}$ & $\frac{\ket{1}+\ket{2}}{\sqrt{2}}$ & $\frac{\ket{1}+\rmi\ket{2}}{\sqrt{2}}$ & \ldots\tabularnewline\addlinespace
\midrule
\addlinespace
\addlinespace
$\mu_{1}\left(\proj{\Psi}\right)$ & $\frac{1}{2}$ & $\frac{1}{2}$ & $0$ & $1$  & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & \ldots\tabularnewline\addlinespace
\addlinespace
\addlinespace
$\mu_{2}\left(\proj{\Psi}\right)$ & $\frac{1}{2}$ & $0$ & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{2}$ & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & \ldots\tabularnewline\addlinespace
\bottomrule
\addlinespace
\end{tabular}
\end{table}

@@

local Bloch sphere embedded in $\mathbb{R}^{3}$. One may, therefore,

@@

We now implement these procedures to enumerate the maximally entangled
states for the specific cases for $n=2,3$ and compare these to the
counts for product states. We have verified explicitly in Eq.~(\ref{eq:CountUnentangledStates})
that the numbers of unit-norm product states for $n=2$, $p=\{3,7,11,19,\ldots\}$
are 
\begin{equation}
(p+1)p^{2}(p-1)^{2}=\{144,14\,112,145\,200,2339\,280,\ldots\}\,,
\end{equation}
and for general $n$, $(p+1)p^{n}(p-1)^{n}$. The irreducible state
counts are reduced by $(p+1)$, giving 
\begin{equation}
p^{2}(p-1)^{2}=\{36,1764,12\,100,116\,964,\ldots\}\,,
\end{equation}
and in general, for $n$-qubits, there are $p^{n}\left(p-1\right)^{n}$
instances of pure product states.

@@

Let us first note that the range of the quadratic map, $\set{x^{2}\bmod p}{x\in\ff{p}}$,
is always one-half of the non-zero elements of $\ff{p}$, and is the
set of elements with square roots in the field. This is the set of
\emph{quadratic residues}, and the complementary set (the other half
of the non-zero field elements) is the set of \emph{quadratic non-residues}.
For example, in $\ff{7}$, the elements $\left\{ 1,2,4\right\} $
are considered positive as they have the square roots $\left\{ 1,3,2\right\} $
respectively; the remaining elements $\left\{ 3,5,6\right\} $ do
not have square roots in the field. What is interesting is that if
we have a uninterrupted sequence of numbers that are all quadratic
residues, then we can define a \textit{transitive order}, with $a>c$
if $a>b$ and $b>c$, provided $a-b$, $b-c$, and $a-c$ are all
quadratic residues. %
\begin{comment}
\todo{Should we remove the quadratic residue part? Since we never
use take the square roots of numbers in order range later, whether
they are the quadratic residues or not doesn't really matter\ldots}
\end{comment}

@@

Although we couldn't prove there is no discrete Born rule by investigating
QPMFFs alone, we could prove there is no ``sensible'' Born rule
which also satisfies an analog of Proposition~\ref{prop:Born-probability-one}
and~\ref{prop:Born-unitary-invariant}. %
\begin{comment}
\todo{Notice that the notation here and previous is a little bit
different because we dealt with mixed states previously, but pure
states here. Besides, should we explain the physical meaning of these
propositions?}
\end{comment}

>>>>

The part of conventional quantum theory (CQT) used by quantum circuit
model is described by the following:
\begin{enumerate}[label=(\roman{enumi})]
\item \label{enu:-orthonormal-basis}$D$ orthonormal basis vectors for
a Hilbert space of dimension~$D$,
\item \label{enu:probability-amplitude}$D$ complex probability amplitude
coefficients describing the contribution of each basis vector,
\item \label{enu:unitary-matrix}a set of probability-conserving unitary
matrix operators that suffice to describe all required state transformations
of a quantum circuit,
\item \label{enu:measurement-framework}and a measurement framework.
\end{enumerate}
In Sec.~\ref{CQC1qubitBloch.sec}, we focus on the geometric issues
raised by the properties~\ref{enu:-orthonormal-basis} and~\ref{enu:probability-amplitude}
given above for CQT\@. In Sec.~\ref{sec:fuzzy}, we introduce the
important issues of~\ref{enu:measurement-framework} and the foundations
of quantum probability space. The expectation values defined in Sec.~\ref{sec:fuzzy}
will be used to understand the geometry of entangled states in Sec.~\ref{sec:The-geometry-of}.
The property~\ref{enu:unitary-matrix} directly related to quantum
circuits will be introduced later in Chapters~\ref{chap:Unrestricted-Finite-Fields}
and~\ref{chap:DQT=000026DQC} when we dive into quantum algorithms.

@@

For a two-dimensional system, we could easily solve the problem of
reducing the full unit-norm space to its irreducible components $\Hat{a}=\left(X,Y,Z\right)$
characterizing the Bloch sphere. We have just argued that essentially
the same process is possible for $D$-dimensional system: in the abstract
argument, we simply identify the family of coefficients $\left\{ \alpha_{i}\right\} $
as being the same if they differ only by an overall phase $\rme^{\rmi\theta}$.
However in practice, this is not a construction that is easy to realize
in a practical computation. We now outline an explicit algorithm for
accomplishing the reduction to the irreducible $D$-dimensional state
space $\CP{D-1}$; this construction will turn out to be useful for
the validation of our discrete results to follow below.

Given a normalized pure state $\ket{\Psi}=\sum_{i=0}^{D-1}\alpha_{i}\ket{i}$,
a natural quantity characterizing a $D$-dimensional system is its
\textit{density matrix}, $\rho=\op{\Psi}{\Psi}$, or 
\begin{equation}
\rho=\begin{pmatrix}|\alpha_{0}|^{2} & \alpha_{0}\alpha_{1}^{*} & \cdots & \alpha_{0}\alpha_{D-1}^{*}\\
\alpha_{1}\alpha_{0}^{*} & |\alpha_{1}|^{2} & \cdots & \alpha_{1}\alpha_{D-1}^{*}\\
\vdots & \vdots & \ddots & \vdots\\
\alpha_{D-1}\alpha_{0}^{*} & \cdots & \alpha_{D-1}\alpha_{D-2}^{*} & |\alpha_{D-1}|^{2}
\end{pmatrix}\,.\label{nqDensity.eq}
\end{equation}
We can now use the complex generalization of the classical Veronese
coordinate system for projective geometry to remove the overall phase
ambiguity $\rme^{\rmi\theta}$ from the $D$-dimensional states. If
we take a particular weighting of the elements of the density matrix~$\rho$,
we can construct a \textit{unit vector} of real dimension $D^{2}$
with the form: 
\begin{equation}
\Hat{a}=\left(|\alpha_{i}|^{2},\ldots,\sqrt{2}\,\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*},\ldots,\sqrt{2}\,\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*},\ldots\right)\,,\label{nqCoords.eq}
\end{equation}
where 
\[
\Hat{a}\cdot\Hat{a}=\sum_{i=0}^{D-1}\left(\left|\alpha_{i}\right|^{2}\right)^{2}+\sum_{i=0}^{D-1}\sum_{\substack{j=0\\
j\ne i
}
}^{D-1}\left(\mathrm{Re}\ \alpha_{i}\alpha_{j}^{*}\right)^{2}+\left(\mathrm{Im}\ \alpha_{i}\alpha_{j}^{*}\right)^{2}=\left(\sum_{i=0}^{D-1}\left|\alpha_{i}\right|^{2}\right)\left(\sum_{j=0}^{D-1}\left|\alpha_{j}\right|^{2}\right)=1\,.
\]
This construction gives an explicit embedding of the $\left(D-1\right)$-dimensional
complex, or $\left(2D-2\right)$-dimensional real, object in a real
space of dimension $D^{2}$. However, this is somewhat subtle because
the vector is of unit length, so technically the embedding space is
a sphere of dimension $D^{2}-1$ embedded in $\R^{D^{2}}$. For example,
the two-dimensional irreducible states could be represented in a four-dimensional
embedding, but the magnitude of every coordinate would be one. Furthermore,
the object embedded in the resulting $\Sphere{3}$ is indeed $\Sphere{2}$
because we can fix one complex coordinate to be unity, and let one
vary, giving a total of two irreducible dimensions. In fact, one must
choose \textit{two} coordinate patches, one covering one pole of $\Sphere{2}$
with coordinates $\alpha_{0}=1+\rmi0$ and $\alpha_{1}=x_{1}+\rmi y_{1}$,
and the other patch covering the other pole of $\Sphere{2}$ with
coordinates $\alpha_{0}=x_{0}+\rmi y_{0}$ and $\alpha_{1}=1+\rmi0$.
\begin{comment}
\todo{Explain the last part clearer or add a picture.}
\end{comment}

@@

One special feature of quantum experiments is that the probabilities
in different experiments are correlated. Consider another experiment
sending exactly the same particle as the previous one but using a
different beam splitter corresponding to the observable $\mathbf{O}_{1}$
with spectral decomposition $\mathbf{O}_{1}=0\,\proj{\ps}+1\,\proj{\ms}+2\,\proj{2}$,
where $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ and $\ket{\ms}=\frac{\ket{0}-\ket{1}}{\sqrt{2}}$.
Although the sample space $\Omega_{1}=\left\{ \ket{\ps},\ket{\ms},\ket{2}\right\} $
and the probability measure $\mu_{1}\colon2^{\Omega_{1}}\rightarrow\left[0,1\right]$
defined by this experiment is different from the previous one, these
two experiments may produce the same post-experimental state~$\ket{2}$,
and the probability of the common event $\left\{ \ket{2}\right\} $
is believed to be the same, i.e., 
\begin{equation}
\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)\,.\label{eq:mu0-equal-mu1}
\end{equation}
In general, as long as sending the same particle, the probability
of the same event in different experiments should always be the same.
This fact is equivalent to the fact that commuting observables could
be measured simultaneously which is essential to define contextuality
and will be explained in Sec.~\ref{sec:Kochen-Specker}.

Since the probability induced by the different beam splitters are
correlated, it is more natural to define one quantum event space~$\events$
containing all possible classical event spaces using different beam
splitters. However, simply taking the union of all event spaces is
a bad idea because two events might appear different but representing
the same situation. For example, if we take the complement on both
sides of Eq.~(\ref{eq:mu0-equal-mu1}), we will have
\begin{equation}
\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
\end{equation}
that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same, and
these events should be identified as the same quantum event to simplify
our discussion. This identification can be achieved by mapping a classical
event~$E$ to the projector generated by $E$,
\begin{equation}
\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\label{eq:pullback-function}
\end{equation}
with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$, because
$\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)$ is equal to
$\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)$ as operators,
\begin{equation}
\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)=\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}=\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,.
\end{equation}
In general, if two classical events~$E$ and $E'$ are mapped to
the same projector, i.e., $\varphi\left(E\right)=\varphi\left(E'\right)$,
then the probability of $E$ is the same as the probability of $E'$.
Therefore, for any classical event~$E$, its corresponding quantum
event is defined to be the projector $\varphi\left(E\right)$, and
the set of all projectors on a given Hilbert space is called a quantum
event space~$\events$. %
\begin{comment}
\todo{Check the citation of this part. Did von Neumann really think
about this when he uses projectors to formulate the quantum theory?}
\end{comment}

@@

\begin{proof}By Eqs.~(\ref{eq:quantum-expectation}), (\ref{eq:pullback-function}),
and (\ref{eq:classical-pullback}), we have
\[
\expval{\mathbf{O}}_{\mu}=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(\proj{i}\right)=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(\varphi\left(\left\{ \ket{i}\right\} \right)\right)=\sum_{i=0}^{D-1}\lambda_{i}\left(\varphi^{*}\mu\right)\left(\left\{ \ket{i}\right\} \right)=\int\left(\varphi^{*}\mathbf{O}\right)\rmd\left(\varphi^{*}\mu\right)\,.
\]
\end{proof}

@@

After introducing quantum probability measures, we might follow the
convention to introduce the Born rule which is the only way corresponding
a state to a quantum probability measure in CQT\@. However, since
the variants of quantum probability measures in Sec.~\ref{sec:Toward-IVPM}
and Chapter~\ref{chap:QIVPM} could not be constructed by a ``Born
rule'' easily, searching for a Born rule step-by-step here might
provide a better idea of what we should do in Sec.~\ref{sec:Toward-IVPM}
and Chapter~\ref{chap:QIVPM}. While the situations will become more
delicate in the later sections, we will fortunately find the unique
Born rule for CQT here.

@@

Let a pure unnormalized state $\ket{\Phi}\in\mathcal{H}$ characterize
the particle sending to a Stern-Gerlach type experiment, and $\muB_{\Phi}$
be the quantum probability measure of the resulting events sensibly
corresponding to $\ket{\Phi}$. For a correspondence $\ket{\Phi}\mapsto\muB_{\Phi}$
to be sensible, we hope that if the state~$\ket{\Phi}$ is one of
the outcomes of a quantum event~$P$, $P\ket{\Phi}=\ket{\Phi}$,
then the event~$P$ always happens, 
\begin{equation}
\muB_{\Phi}\left(P\right)=1\,,\label{eq:Born-probability-one}
\end{equation}
and vice versa. Moreover, since the physical phenomena exist and should
be the same no matter how we describe them, the probability of an
event should be invariant despite how we choose the basis. Because
changing to another basis is the same as applying a unitary map~$U$,
we should have 
\begin{equation}
\muB_{U\ket{\Phi}}\left(UPU^{\dagger}\right)=\muB_{\Phi}\left(P\right)\,.\label{eq:Born-unitary-invariant}
\end{equation}
It is easy to check that the correspondence satisfying these conditions
is unique, 
\begin{equation}
\muB_{\Phi}(P)=\frac{\melem{\Phi}{P}{\Phi}}{\ip{\Phi}{\Phi}}\label{eq:Born}
\end{equation}
and called the Born rule \cite{Born1983,Mermin2007,Jaeger2007}. If
$\ket{\Phi}$ is normalized, Eq.~(\ref{eq:Born}) could be simplified
as $\muB_{\Phi}(P)=\melem{\Phi}{P}{\Phi}$. Since a mixed state $\rho=\sum_{j=1}^{N}q_{j}\proj{\Phi_{j}}$
is a weighted average of projectors $\proj{\Phi_{j}}$ with weights
$q_{j}>0$ and $\sum_{j=1}^{N}q_{j}=1$, the generalized Born rule
of $\rho$, $\muB_{\rho}\left(P\right)$, is also a weighted average
of $\muB_{\Phi_{j}}\left(P\right)$, 
\begin{equation}
\muB_{\rho}\left(P\right)=\sum_{j=1}^{N}q_{j}\muB_{\Phi_{j}}\left(P\right)=\Tr\left(\rho P\right)\,,\label{eq:mixed-Born}
\end{equation}
which is also a quantum probability measure and consistent with Gleason's
theorem.

As an example, consider a three-dimensional Hilbert space with orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $ and the observable
$\mathbf{O}_{0}$ defined in Eq.~(\ref{eq:observable}). Two fragments
of valid probability measures~$\mu_{1}$ and $\mu_{2}$ that can
be associated with this space are defined in Table~\ref{tab:quantum-probability-measure}.
By the Born rule, the first probability measure corresponds to the
quantum system being in the pure state $\ket{\ps}=\frac{\ket{0}+\ket{1}}{\sqrt{2}}$
and the second corresponds to the quantum system being in the state
$\frac{\proj{0}+\proj{2}}{2}$. The expectation values of the observable
$\mathbf{O}$, $\expval{\mathbf{O}}_{\mu_{1,2}}$, are $1.5$ in the
first case and $2$ in the second. The quantum expectation value can
also be used to decide whether a state is entangled or not for multipartite
systems as we describe in the following section.
\begin{table}
\noindent \begin{centering}
\caption{\label{tab:quantum-probability-measure}Two fragments of valid probability
measures~$\mu_{1}$ and $\mu_{2}$.}
\par\end{centering}
\noindent \centering{}%
\begin{tabular}{ccccccccccc}
\toprule 
\addlinespace
$\ket{\Psi}$ & $\ket{0}$ & $\ket{1}$ & $\ket{2}$ & $\frac{\ket{0}+\ket{1}}{\sqrt{2}}$ & $\frac{\ket{0}+\rmi\ket{1}}{\sqrt{2}}$ & $\frac{\ket{0}+\ket{2}}{\sqrt{2}}$ & $\frac{\ket{0}+\rmi\ket{2}}{\sqrt{2}}$ & $\frac{\ket{1}+\ket{2}}{\sqrt{2}}$ & $\frac{\ket{1}+\rmi\ket{2}}{\sqrt{2}}$ & \ldots\tabularnewline\addlinespace
\midrule
\addlinespace
\addlinespace
$\mu_{1}\left(\proj{\Psi}\right)$ & $\frac{1}{2}$ & $\frac{1}{2}$ & $0$ & $1$  & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & \ldots\tabularnewline\addlinespace
\addlinespace
\addlinespace
$\mu_{2}\left(\proj{\Psi}\right)$ & $\frac{1}{2}$ & $0$ & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & $\frac{1}{2}$ & $\frac{1}{2}$ & $\frac{1}{4}$ & $\frac{1}{4}$ & \ldots\tabularnewline\addlinespace
\bottomrule
\addlinespace
\end{tabular}
\end{table}

@@

local Bloch sphere embedded in $\mathbb{R}^{3}$. Therefore, one may

@@

We now implement these procedures to enumerate the maximally entangled
states for the specific cases for $n=2,3$ and compare these to the
counts for product states. We have verified explicitly in Eq.~(\ref{eq:CountUnentangledStates})
that the numbers of unit-norm product states for $n=2$, $p=\{3,7,11,19,\ldots\}$
are 
\begin{equation}
(p+1)p^{2}(p-1)^{2}=\{144,14\,112,145\,200,2339\,280,\ldots\}\,,
\end{equation}
and for general $n$, $(p+1)p^{n}(p-1)^{n}$. The irreducible state
counts are reduced by $(p+1)$, giving 
\begin{equation}
p^{2}(p-1)^{2}=\{36,1764,12\,100,116\,964,\ldots\}\,,
\end{equation}
and in general for $n$-qubits, there are $p^{n}\left(p-1\right)^{n}$
instances of pure product states.

@@

Let us first note that the range of the quadratic map, $\set{x^{2}\bmod p}{x\in\ff{p}}$,
is always one-half of the non-zero elements of $\ff{p}$, and is the
set of elements with square roots in the field. This is the set of
\emph{quadratic residues}, and the complementary set (the other half
of the non-zero field elements) is the set of \emph{quadratic non-residues}.
For example in $\ff{7}$, the elements $\left\{ 1,2,4\right\} $ are
considered positive as they have the square roots $\left\{ 1,3,2\right\} $
respectively; the remaining elements $\left\{ 3,5,6\right\} $ do
not have square roots in the field. What is interesting is that if
we have a uninterrupted sequence of numbers that are all quadratic
residues, then we can define a \textit{transitive order}, with $a>c$
if $a>b$ and $b>c$, provided $a-b$, $b-c$, and $a-c$ are all
quadratic residues. %
\begin{comment}
\todo{Should we remove the quadratic residue part? Since we never
use take the square roots of numbers in order range later, whether
they are the quadratic residues or not doesn't really matter\ldots}
\end{comment}

@@

Although we couldn't prove there is no discrete Born rule by investigating
QPMFFs alone, we could prove there is no ``sensible'' Born rule
which also satisfies an analog of Eqs.~(\ref{eq:Born-probability-one})
and~(\ref{eq:Born-unitary-invariant}). %
\begin{comment}
\todo{Notice that the notation here and previous is a little bit
different because we dealt with mixed states previously, but pure
states here. Besides, should we explain the physical meaning of these
propositions?}
\end{comment}
